Dynamic Load Balancing for\\Heterogeneous Systems

### 2011-12-05 paper/paper.tex
Added to APU section.

\subsection{APU Architecture}
The APU is a relatively new, novel architecture that attempts to 
improve on the the discrete CPU+GPU system.  The CPU die is split
between the typical CPU processor as well as allocating space
for a SIMD engine, the basis for a GPU processor.  The APU has a 
shared memory between the CPU and SIMD engine, in which accesses
are facilitated through a high-speed memory controller.  The AMD
Fusion technology is an example of this type of architecture~\cite{AMDFusion}.

One of the main benefits of the APU is the elimination of the PCI-e
bus, which allows for much faster transfer between CPU and GPU.  Daga et al.
show that the AMD Fusion architecture allows for much faster data transfers
between CPU and GPU, allowing for an overall improvement in runtime, despite
reduced compute power on the GPU~\cite{Daga2011}.

@@

When analyzing the results, we considered the possibility that the CPU and GPU kernels were
actually running in serial, which would explain the performance trends we were seeing in our
static and dynamic load balancing schemes.  An AMD profiler was used to find out the times each
kernel took to compute, and the sum of these times was compared to the actual runtime of the
benchmark.  We found that the actual runtime of the benchmark was typically slightly more than
the sum of the runtimes of each kernel, which seemed to indicate that the kernels were indeed
running serially, with some overhead for data transfer times.

>>>>

\subsection{APU Architecture}
The APU is a relatively new, novel architecture that attempts to 
improve on the the discrete CPU+GPU system.  The CPU die is split
between the typical CPU processor as well as allocating space
for a SIMD engine, the basis for a GPU processor.  The APU has a 
shared memory between the CPU and SIMD engine, in which accesses
are facilitated through a high-speed memory controller.  The AMD
Fusion technology is an example of this type of architecture~\cite{AMDFusion}.
Because of the limited space on the CPU die, the overall performance
capabilities of the CPU and GPU are often more limited than on a traditional 
discrete CPU and GPU architecture.

One of the main benefits of the APU is the elimination of the PCI-e
bus, which allows for much faster transfer between CPU and GPU.  Daga et al.
show that the AMD Fusion architecture allows for much faster data transfers
between CPU and GPU, allowing for an overall improvement in runtime, despite
reduced compute power on the GPU~\cite{Daga2011}.  The improvment of the 
data transfer times greatly improves the applicability of the GPU for use
in general computing paradigms, specifically that of CPU+GPU co-processing.
Decreasing the data trasnsfer time reduces the penalty associated with migrating
computation to the GPU, and therefore can access the computation of the GPU
more at will then in discrete GPUs which are bound by the slow access speeds
of the PCI-e bus.

@@

When analyzing the results, we considered the possibility that the CPU and GPU kernels were
actually running in serial, which would explain the performance trends we were seeing in our
static and dynamic load balancing schemes.  An OpenCL profiler was used to find out the times each
kernel took to compute, and the sum of these times was compared to the actual runtime of the
benchmark.  We found that the actual runtime of the benchmark was typically slightly more than
the sum of the runtimes of each kernel, which seemed to indicate that the kernels were indeed
running serially, with some overhead for data transfer times.
